---
title: "Assignment_Lesson7"
format: html
editor: visual
---

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(reactable)
library(plotly)
library(crosstalk)
```

df <- data.frame(
  movie1 =c(5, 1, 4, NA, NA, NA, 2, 1),
  movie2= c(5, NA, 3, 2, 5, NA, 2, 1),
  movie3= c(1, 4, 2, 5, 2, NA, 5, 4),
  movie4 = c(4, 2, NA, 1, 5, 2, 3, 3)
)
mean_u2<-mean(df$movie2, na.rm=TRUE)
mean_u4<-mean(df$movie4, na.rm=TRUE)
pre<-mean_u2+(df$movie4[6]-mean_u4)
pre
```

```{r}

for(i in 2:8){
  a<-as.numeric(df[1, ])
  b<-as.numeric(df[i,])
  ok<-complete.cases(a,b)
  if(sum(ok)<2) next
  print(c(movie=i, correlation=cor(a[ok], b[ok])))
}

```

```{r}

library(dplyr)
countries<-read.csv("http://manctsui.github.io/datasets/countries.csv")
filled<-countries|>
  group_by(Region)|>
  mutate(
    Agriculture=ifelse(is.na(Agriculture),
                       mean(Agriculture, na.rm=TRUE), Agriculture),
    Industry=ifelse(is.na(Industry),
                     mean(Industry, na.rm=TRUE), Industry)
  )|>
  ungroup()
filled
```

```{r}


library(dplyr)
countries<-read.csv("http://manctsui.github.io/datasets/countries.csv")
countries|>
  group_by(Region)|>
  summarise(
    Agriculture_na=sum(is.na(Agriculture)),
    Industry_na=sum(is.na(Industry))
  )

```

```{r}

df <- data.frame(
  temp = c(79, 74, 73, 76, 82, 72, 71, 79, 83, 70, 73, 75, 77),
  chirps = c(44, 40, 38, 43, 48, 37, 34, 45, 51, 32, 35, 42, 43)
)
cor(df$temp, df$chirps)
mean(df$temp)
sd(df$temp)
mean(df$chirps)
sd(df$chirps)
slope<- cor(df$temp, df$chirps)*sd(df$temp)/sd(df$chirps)
intercept<-mean(df$temp)-slope*mean(df$chirps)
slope
intercept
#Let x=chirps, y=temp.
#Slope is: b1=cor(temp, chirps)*sd(temp)/sd(chirps)
 #           =0.970876*4.110649/5.589597
  #          =0.7139926
#Intercept is:b0=mean(temp)-b1*mean(chirps)
 #           =75.69231-(0.7139926*40.92308)
  #          =46.47353
#Predicted temp=46.47353+0.714*chirps.

  
```
